Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-08 paper/paper_new.tex
Updates from Overleaf

Our ultimate goal is to create a generalized process that works on classes of specimen images. For the BGNN project we are beginning with fish images, but we are designing the metadata generation system so that it can eventually operate on other species if appropriately  trained. To accomplish this, a much larger training dataset consisting of more diverse images will be required. The first step towards greater generality will be to operate on other fish collections besides INHS, which is something our program has already
shown itself capable of doing during initial testing. Another requirement will be to generalize the ruler reading process beyond the INHS-specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits.
% Todo: Are these worth mentioning?
%Adding things like seahorses and eels.
%Fitting a ``spine'' to specimen.
%\section{Conclusion}
%\textbf{Todo}

>>>>

Our longer-term goal is to create a generalized process that works on classes of specimen images. For the BGNN project we are beginning with fish images, but we are designing the metadata generation system so that it can eventually operate on other species if appropriately  trained. To accomplish this, a much larger training dataset consisting of more diverse images will be required. The first step towards greater generality will be to operate on other fish collections besides INHS, which is something our program has already
shown itself capable of doing during initial testing. Another requirement will be to generalize the ruler reading process beyond the INHS-specific reading of digits on the ruler, which will likely involve an automated method of reading ruler ticks instead of digits. Overall, the  research reported in this paper will improve our BGNN workflow, and at the same time demonstrates an innovative approach that may greatly enhance digital  library  services for the tens of thousands of digitized specimens and images for other types of objects.
% Todo: Are these worth mentioning?
%Adding things like seahorses and eels.
%Fitting a ``spine'' to specimen.
%\section{Conclusion}
%\textbf{Todo}
